Fish do not need Visas: the transboundary nature of world fished species

### 2019-11-26 Manuscript_Draft.Rmd
FIrst manuscript draft shared with Colette and Gabriel

---
title: "Fish do not need Visas: the transboundary nature of world fished species"
author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, William W.L. Cheung^1^"
date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^ Yale"
subtitle: "DRAFT DO NOT SHARE"
# subtitle: "Fish do not need Visas (16/40 character maximum)"
output:
  word_document:
    # reference_docx: ./Manuscript_Instructions/science_template.docx
  pdf_document:
    fig_caption: yes
geometry: margin=1in
editor_options:
  chunk_output_type: console
# bibliography: ./References/FishForVisa_Ref.bib
# csl: ./References/science.csl
---

@@

In here, we overlap the known distribution of **968** marine fish species with **256** Economic Exclusive Zones of the world to map the number of transboundary species and and their contribution to global catch and landed value. We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@TEH].

@@

As Caddy (1997) pointed out, virtually all coastal nations share at least one transboundary species with their neighbors with some sharing over 100 species with surrounding EEZs (Fig. 1). With the current state of knowledge of fished species and their distributions, we estimate a total of `r Total_trans_n` transboundary species in the world, more than double of what had been previously estimated [@Teh:2015gd]. These fisheries are important in terms of both landings and revenue. In the last ten years, the global fleet has landed an average of XXX tones, generating USD `r Total_Trans_Rev` million in fishing revenue from shared stocks fished within EEZs. This represents **XX**% of the global catch and `r round(Per_Trans_Rev,2)`% of total revenue generated by those fisheries in all EEZs of the world. All these values are higher than previously estimated [@Teh]. The importance of these species exceeds in EEZs like the United States where **XX** species are responsible for up to **XX** millions USD and Peru where **17** species are responsible for XXX million USD (Fig 1). Transboundary fisheries are vast and economically important in regions with historic fisheries-related conflicts. The Asian region has seen 43.0% of all international fisheries conflicts since 2000; Europe, where 11.5% of fishing conflicts occur since 1974s [@Spijkers:2019cz], has been involved in a conflict between Ireland and the European Union over mackerel since 2007 [@Spijkers:2017ij], and finally, the Mediterranean has seen conflicts since the 1980's [@Kliot:1989kv]. The identification of current transboundary species is a first step towards establishing joint management plan of marine resources [@Link:2010ei], key to not only sustain fisheries but also avoid international conflict.

@@

data.frame(Stock_Status,
           Rules) %>% 
  kable("latex", booktabs = T,
        caption = "Rules to determine the status of each transboundary species") %>%
  kable_styling(full_width = F) %>%
  column_spec(1,width = "3cm") %>% #wraps text in column2
  column_spec(2,width = "13cm") #%>% #wraps text in column2

>>>>

---
title: "Fish do not need Visas: the transboundary nature of world fished species"
author: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, William W.L. Cheung^1^"
date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^ Yale"
subtitle: "DRAFT DO NOT SHARE"
# subtitle: "Fish do not need Visas (16/40 character maximum)"
output:
  word_document:
    # reference_docx: ./Manuscript_Instructions/science_template.docx
  pdf_document:
    fig_caption: yes
geometry: margin=1in
editor_options:
  chunk_output_type: inline
# bibliography: ./References/FishForVisa_Ref.bib
# csl: ./References/science.csl
---

@@

In here, we overlap the known distribution of **968** marine fish species with 248 Economic Exclusive Zones of 175 countries to map the number of transboundary species and and their contribution to global catch and landed value. We adopted the UN definition of transboundary stocks (shared by neighboring EEZs) but carried the analysis at the species level, rather than stocks (populations within a species), due to lack of stock-specific spatial and ecological information on all of the fished species [@TEH].

@@

As Caddy (1997) pointed out, virtually all coastal nations share at least one transboundary species with their neighbors with some sharing over 100 species with surrounding EEZs (Fig. 1). With the current state of knowledge of fished species and their distributions, we estimate a total of 633 transboundary species in the world, more than double of what had been previously estimated [@Teh:2015gd]. These fisheries are important in terms of both landings and revenue. In the last ten years, the global fleet has landed an average of XXX tones, generating USD 79.7 million in fishing revenue from shared stocks fished within EEZs. This represents **X**% of the global catch and 49.8% of total revenue generated by those fisheries in all EEZs of the world. All these values are higher than previously estimated [@Teh]. The importance of these species exceeds in EEZs like the United States where 116 species are responsible for up to 12.20 millions USD and Peru where 28 species are responsible for USD 5.2 million  (Fig 1). Transboundary fisheries are vast and economically important in regions with historic fisheries-related conflicts. The Asian region has seen 43.0% of all international fisheries conflicts since 2000; Europe, where 11.5% of fishing conflicts occur since 1974s [@Spijkers:2019cz], has been involved in a conflict between Ireland and the European Union over mackerel since 2007 [@Spijkers:2017ij], and finally, the Mediterranean has seen conflicts since the 1980's [@Kliot:1989kv]. The identification of current transboundary species is a first step towards establishing joint management plan of marine resources [@Link:2010ei], key to not only sustain fisheries but also avoid international conflict.

@@

data.frame(Stock_Status,
           Rules) %>% 
  kable(, booktabs = T,
        caption = "Rules to determine the status of each transboundary species") %>%
  kable_styling(full_width = F) %>%
  column_spec(1,width = "3cm") %>% #wraps text in column2
  column_spec(2,width = "13cm") #%>% #wraps text in column2
